Flatiron cleaning

### 2022-01-05 Rmd/rdi analysis.Rmd
Update HR with strata

**We have `r clinical_data %>% distinct(patientid) %>% nrow()` patients info in clinical data.  
**We have `r drugs %>% distinct(PatientID) %>% nrow()` patients info in clinical data.

```{r drugs episode cleanup}
drugs <- drugs %>% 
  `colnames<-`(str_to_lower(colnames(.))) %>% 
  # Select only records for administration
  filter(episodedatasource == "Administrations") %>%
  # bind with clinical
  inner_join(., clinical_data, 
          by = "patientid") %>% 
  arrange(patientid, episodedate)
```
But when merged both data, we have `r drugs %>% distinct(patientid) %>% nrow()` patients with clinical informations who received drugs.

@@

(hold on to the thought that what I call `target_auc` include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and paclitaxel, they are just present in the same column called `target_auc` for a tidy data organisation - You can find the calculations formula at the end of the document)  
When I bind the data together (drug + corresponding creatinine + ...), I take the closest date of creatinine, height, weight, BSA, AUC, from the cycle date to calculate `target_auc` for Carboplatin, and paclitaxel and their `expected_dose`. It can be days in between but it can also be more.

@@

- Exclude patients that received wrong dose dense of 1 carbo + 2 paclitaxels
```{r}
Frontline_adjusted <- standard_care %>% 
  filter(is.na(wrong_pacli_dosedense))

@@

## Univariable
```{r Table 6 HR}
# tbl2 <- Frontline %>%
#   filter(therapy == "Upfront Chemo")
# tbl1 <- tbl2 %>%
#   select(vital_status, RDI_carbo_neo, RDI_carbo_neo_grp) %>% 
#   tbl_uvregression(method = survival::coxph,
#                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>% 
#   add_
# tbl2 <- tbl2 %>%
#   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
#   tbl_uvregression(method = survival::coxph,
#                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# 
# 
# tbl3 <- Frontline %>%
#   filter(therapy == "Upfront Surgery")
# tbl3 <- tbl3 %>%
#   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
#   tbl_uvregression(method = survival::coxph,
#                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)),
#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# tbl5 <- tbl_merge(list(tbl2, tbl3))
# 
# # tbl4 <- tbl_merge(list(tbl4_1, tbl4_2)) %>%
# #   modify_spanning_header(everything() ~ NA_character_)
# 
# tbl_stack(list(tbl1, tbl5)) %>%
#   bold_labels() %>%
#   italicize_levels()

  # trial %>%
  # select(age, grade, stage, trt) %>%
  # mutate(grade = paste("Grade", grade)) %>%
  # # tbl_strata(
  # #   strata = grade,
  # #   .tbl_fun =
  # #     ~ .x %>%
  #       tbl_summary(by = trt, missing = "no") %>%
  #       add_n()
  # )

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- tbl2 %>%
  select(vital_status, RDI_carbo_neo, RDI_carbo_neo_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- tbl2 %>%
  select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- tbl3 %>%
  select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- tbl2 %>%
  select(vital_status, RDI_pacli_neo, RDI_pacli_neo_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- tbl2 %>%
  select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- tbl3 %>%
  select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel/Upfront Chemo", 
                           "paclitaxel/Upfront Chemo",
                           "paclitaxel/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
```{r Table 5 HR adjusted rdi group adjusted by other drug}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

PH assumption Upfront Chemo
```{r prop H}
coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2)  %>% 
  cox.zph()
```

PH assumption Upfront Surgery
```{r}
coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
  cox.zph()
```

@@

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking` 
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

PH assumption Upfront Chemo
```{r prop H complete case}
coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2)  %>% 
  cox.zph()
```

PH assumption Upfront Surgery
```{r}
coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
  cox.zph()
```

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology` 
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl2, tbl3),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

>>>>

**We have `r clinical_data %>% distinct(patientid) %>% nrow()` patients info in clinical data.  
**We have `r drugs %>% distinct(PatientID) %>% nrow()` patients info in drug data.

```{r drugs episode cleanup}
drugs <- drugs %>% 
  `colnames<-`(str_to_lower(colnames(.))) %>% 
  # Select only records for administration
  filter(episodedatasource == "Administrations") %>%
  # bind with clinical
  inner_join(., clinical_data, 
          by = "patientid") %>% 
  arrange(patientid, episodedate)
```
But when merged both data, we have `r drugs %>% distinct(patientid) %>% nrow()` patients with clinical information who received drugs.

@@

(hold on to the thought that what I call `target_auc` include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and paclitaxel, they are just present in the same column called `target_auc` for a tidy data organization - You can find the calculations formula at the end of the document)  
When I bind the data together (drug + corresponding creatinine + ...), I take the closest date of creatinine, height, weight, BSA, AUC, from the cycle date to calculate `target_auc` for Carboplatin, and paclitaxel and their `expected_dose`. It can be days in between but it can also be more.

@@

- Exclude patients that received wrong dose dense of 1 carbo + 2 paclitaxel
```{r}
Frontline_adjusted <- standard_care %>% 
  filter(is.na(wrong_pacli_dosedense))

@@

## Univariable and drug only adjusted analysis
```{r Table 6 HR}
# tbl2 <- Frontline %>%
#   filter(therapy == "Upfront Chemo")
# tbl1 <- tbl2 %>%
#   select(vital_status, RDI_carbo_neo, RDI_carbo_neo_grp) %>% 
#   tbl_uvregression(method = survival::coxph,
#                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>% 
#   add_
# tbl2 <- tbl2 %>%
#   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
#   tbl_uvregression(method = survival::coxph,
#                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# 
# 
# tbl3 <- Frontline %>%
#   filter(therapy == "Upfront Surgery")
# tbl3 <- tbl3 %>%
#   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
#   tbl_uvregression(method = survival::coxph,
#                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)),
#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# tbl5 <- tbl_merge(list(tbl2, tbl3))
# 
# # tbl4 <- tbl_merge(list(tbl4_1, tbl4_2)) %>%
# #   modify_spanning_header(everything() ~ NA_character_)
# 
# tbl_stack(list(tbl1, tbl5)) %>%
#   bold_labels() %>%
#   italicize_levels()

  # trial %>%
  # select(age, grade, stage, trt) %>%
  # mutate(grade = paste("Grade", grade)) %>%
  # # tbl_strata(
  # #   strata = grade,
  # #   .tbl_fun =
  # #     ~ .x %>%
  #       tbl_summary(by = trt, missing = "no") %>%
  #       add_n()
  # )
```

<div class = "row">
<div class = "col-md-6">
```{r Table 61 HR}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- tbl2 %>%
  select(vital_status, RDI_carbo_neo, RDI_carbo_neo_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- tbl2 %>%
  select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- tbl3 %>%
  select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- tbl2 %>%
  select(vital_status, RDI_pacli_neo, RDI_pacli_neo_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- tbl2 %>%
  select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- tbl3 %>%
  select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel/Upfront Chemo", 
                           "paclitaxel/Upfront Chemo",
                           "paclitaxel/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
</div>

<div class = "col-md-6">
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl21 <-
  coxph(Surv(time = tbl2$month_at_os_from_treatment,
             event = tbl2$vital_status
             ) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp,
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status
             ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp,
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
</div>
</div>

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
```{r Table 5 HR adjusted rdi group adjusted by other drug}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(imp_stagecat) + strata(histology) + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

PH assumption Upfront Chemo
```{r prop H}
coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status
           ) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, 
      data =  tbl2)  %>% 
  cox.zph()
```

PH assumption Upfront Surgery
```{r}
coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(imp_stagecat) + strata(histology) + imp_debulking, data =  
        tbl3) %>%
  cox.zph()
```

@@

## Univariable and drug only adjusted analysis

<span style="color:green">**Table  HR Univariable**</span>

<div class = "row">
<div class = "col-md-6">
```{r Table  HR}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo", !is.na(stagecat), !is.na(debulking))
tbl1 <- tbl2 %>%
  select(vital_status, RDI_carbo_neo, RDI_carbo_neo_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- tbl2 %>%
  select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery", !is.na(stagecat), !is.na(debulking))
tbl3 <- tbl3 %>%
  select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo", !is.na(stagecat), !is.na(debulking))
tbl1 <- tbl2 %>%
  select(vital_status, RDI_pacli_neo, RDI_pacli_neo_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- tbl2 %>%
  select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery", !is.na(stagecat), !is.na(debulking))
tbl3 <- tbl3 %>%
  select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel/Upfront Chemo", 
                           "paclitaxel/Upfront Chemo",
                           "paclitaxel/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
</div>

<div class = "col-md-6">
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo", !is.na(stagecat), !is.na(debulking))
tbl21 <-
  coxph(Surv(time = tbl2$month_at_os_from_treatment,
             event = tbl2$vital_status
             ) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp,
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery", !is.na(stagecat), !is.na(debulking))
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status
             ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp,
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
</div>
</div>

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking` 
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%

  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status
             ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(stagecat) + strata(histology) + debulking, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

PH assumption Upfront Chemo
```{r prop H complete case}
coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status
           ) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, 
      data =  tbl2)  %>% 
  cox.zph()
```

PH assumption Upfront Surgery
```{r}
coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(stagecat) + strata(histology) + debulking, 
      data =  tbl3) %>%
  cox.zph()
```

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology` 
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl2, tbl3),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<br>
<br>
